---
title: "About me"
site: distill::distill_website
description: |
  Alexander Dernild
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

As a part of my journey towards learning Data Science, I have created this website/blog to showcase my projects, articles and other good stuff. If you have any questions about any of the content on this site, feel free to contact me at alex@dernild.dk.

My name is Alexander Dernild, I'm 24 years old and from Denmark. I have a bachelor's degree in Sociology and Cultural Analysis and I'm currently pursuing a master's degree in Data Science, with the specialization Human Informatics at University of Southern Denmark.

#### Academic interests

My academic interests include but are not limited to: Cultural Sociology, Sociology of Everyday Life, Environmental Sociology, Computational Linguistics, Computational methods for Social Sciences & Philosophical underpinnings of Social Sciences research.

***

```{=html}
```{r, echo=FALSE, results='asis'}
xfun::file_string('timeline.html')
```
```
