---
title: "About me"
site: distill::distill_website
description: |
  Alexander Dernild
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

Hi and welcome to this site! My name is Alexander Dernild and I'm a master's student from Denmark. I hold a bachelor's degree in Sociology and Cultural Analysis and am currently pursuing a master's degree in Data Science, specializing in Human Informatics at University of Southern Denmark.

As a part of my journey towards learning Data Science, I have created this website/blog to showcase my projects, articles and other good stuff. If you have any questions, feedback or concerns, about any of the content on this site, feel free to contact me at alex@dernild.dk.

#### Academic interests

My academic interests include but are not limited to: Cultural Sociology, Sociology of Everyday Life, Environmental Sociology, Computational Linguistics, Computational methods for Social Sciences & Philosophical underpinnings of Social Sciences research.

***

```{=html}
```{r, echo=FALSE, results='asis'}
xfun::file_string('timeline.html')
```
```
